\chapter{Consensus}\label{ch:consensus}
{
    \section{Introduction}
     {
      Previous Chapters discuss the scientific and technical aspects of CityScope, demonstrating how it can improve, expedite, and simplify complex urban processes. This last chapter concludes the \textit{New Urban Process} with the goal of using CityScope to establish consensus and agreement between diverse stakeholders. Too often, planning processes envision urban futures through data, simulation, and design iterations, but fail to include stakeholders and the general public as active voices in the decision-making \cite{Innes2016}. This is the byproduct of the length, complexity, and cost of traditional urban processes, as well as the fear of uncertainty and `anarchism' associated with the involvement of the masses \cite{banerjee2011companion}. In a traditional process, \textit{``the tasks are linear, and the players have separate and distinct responsibilities...(it) emphasizes getting the ``best'' and most objective information about an issue and using deductive logic to move from goals to choices.''} \cite{Innes2016} This status quo is deeply rooted in the assumption that the public is not necessarily aware or otherwise capable of comprehending the issues being addressed. With the immense flow of information, access to knowledge, and the ability to become a `citizen export' \cite{banerjee2011companion}, these notions are becoming obsolete in 21\textsuperscript{st} century urban-planning.


      \subsection{Citizen Participation}
      {
          As mentioned in Chapter \eqref{intro:challanges-processes}, even in democratic regimes, over-bureaucratization, privatization, and self-interests can create mistrust and discourage citizens from `real' involvement. In 1969, Arnstein proposed the `Ladder of Citizen Participation', a tool for evaluating and improving the engagement between citizens and stakeholders. Arnstein aimed to reflect on the range of participatory practices by inquiring - \textit{``What is citizen participation?...It is the redistribution of power that enables the have-not citizens, presently excluded...to be deliberately included in the future. It is the strategy by which the have-nots join in determining how information is shared, goals and policies are set...participation without redistribution of power is an empty and frustrating process.''} \cite{arnstein1969ladder}
      }

      \subsection{Resolving Impasses}
      {
          Arnstein's Ladder features eight `rungs' that describe three general forms of citizen power in decision-making: Nonparticipation (no power), Degrees of Tokenism (counterfeit power), and Citizen Power (actual power). Arenstein concluded that in many cases, participation ends within the bounds of tokenism, where citizens are either under the false perception of power-sharing, or are merely informed as passive observers. In higher levels of participation, \textit{``power is in fact redistributed through negotiation between citizens and powerholders. They agree to share planning and decision-making responsibilities through...mechanisms for resolving impasses.''} \cite{arnstein1969ladder}
          In this context, participation methods can address the need for \textit{`mechanisms for resolving impasses'}, which are set to reduce the friction between the public and decision-makers when providing equal access to information. The path leading form `passive' to `active' participation, can be achieved by the introduction of personal-learning and self-discovery \cite{bulmer_how_2001}. These promote the development of active learning and engagement systems, which bring participants to the center of the decision-making process.
      }

      \subsection{Collaborative Participation}
      {
          When moving from informing or consultation to active participation, the decision-making process gains the public's collective wisdom, while the public itself is empowered to make informed decisions \cite{innes2010planning}. This type of `Collaborative Participation' can gain from the usage of new tools, technologies, and data, as long as these are designed to facilitate the exchange and scrutiny of their own processes. As Inness concluded, \textit{``The potential for...adapting knowledge technologies to work for citizens is bounded only by our imaginations and possible only if technology itself is partially shaped by its users... we need to learn to take advantage of knowledge technologies for collaborative processes. To do so successfully will require that users shape and manipulate the technologies.''}\cite{innes2010planning} In that sense, collaborative platforms can only be viewed as a means to improve the quality of decision-making if the platforms themselves are open for review, evaluation, and even criticism.
      }
     }
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


    \section{Consensus Case Studies}
     {
      From its early prototypes (see Section \eqref{subsec:observatory_discussion}), CityScope development was centered around the engagement of diverse user groups. As explored in Chapter \eqref{ch:transformation}, the design of most CityScope instances followed this concept with user-friendly, accessible, and easily-extendable system. Nevertheless, these technical advantages cannot inherently promote a collaborative and consensus-driven process. Participation can only be viewed as a means to improve the quality of decision-making, if the process, tools, data, and models are themselves open and accessible \cite{Innes2016, innes2010planning}.
      \newline
      Early versions of CityScope evolved from a decades-long effort to create alternatives to traditional planning, design, GIS, and CAD tools \cite{ben-joseph2001, ishii2004bringing, negroponte1975soft, Sutherland1963}. For example, the Urban Observatory \eqref{sec:urbanobservatory}, CityScope Volpe \eqref{sec:cityscope_volpe}, and DeepScope \eqref{sec:deepscope} were all designed as reaction to the increased complexity, labor, and cost involved with traditional tools and their negative impact on urban processes as a whole.
      In 2014, CityScope was firstly suggested as an engagement platform for real-world public participation processes. \textbf{CityScope Boston BRT}, a community engagement and co-creation process for the planning on Bus Rapid Transit routes, brought together a range of UHCI technologies to be used in a public participation campaign. Here, CityScope was not only set as an alternative planning tool, but also as a medium supporting learning, debate, and evidence-based discourse by diverse and sometimes conflicting parties.
      \newline
      Many of the lessons learned in the BRT project, were put into extreme test in the \textbf{FindingPlaces} project. In 2015, the City of Hamburg faced an escalating crisis following a wave of refugees arriving from war zones in the Middle-East. CityScope FindingPlaces was created as part of a city-wide effort to engage the public on where-and-how should refugees be hosted in the future. FindingPlaces included a comprehensive public outreach, dozens of orchestrated community sessions, as well as structured documentation, feedback, and reporting mechanisms.
      \newline
      The rest of this Chapter discusses CityScope projects that demonstrated consensus-building, collaborative planning, co-creation, and learning with diverse stakeholders. It focuses on the role of CityScope within larger urban processes, and the impact it made both on the end-results, as well as the process itself.
     }

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \input{chapters/consensus/BRT/BRT.tex}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \input{chapters/consensus/findingplaces/findingplaces.tex}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \section{Discussion: Consensus Building}\label{sec:cons-decentralizing}
    {
        This chapter discussed CityScope's role in consensus-driven processes for urban decision-making. Previous chapters have shown how CityScope is designed for an evidence-based, iterative, and collaborative planning process; Yet these advantages cannot promise a truly participatory process. In fact, many of the technological features presented in previous chapters might improve the quality of traditional planning, but thus negate a consensus-driven process. For example, an iterative design platform could be used by a planning authority to improve the design outcome of a neighborhood, but it would not be utilized in a public-facing manner; location data might support regulatory amendments, but these data and models might not be accessible to the rest of the community for critical evaluation.
        \newline
        The work presented in this Chapter emphasized the need to coverage the advantages of urban technologies with a public-facing social discourse. As evident from work reviewed in this and prior Chapters, collaborative UHCI systems can only benefit their communities if they themselves are open for review, evaluation, and even criticism. This type of `technological consensus' has the potential to elevate legally-binding public participation towards true partnership and citizen control \cite{arnstein1969ladder, Innes2016}.
    }
}

