%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Kent Larson} 

{Director, City Science Group, Media Lab}
{Massachusetts Institute of Technology}
\subsection*{Biography}

{Kent Larson directs the City Science group at the MIT Media Lab. His research focuses on developing urban interventions that enable more entrepreneurial, livable, high-performance districts in cities. To that end, his projects include advanced simulation and augmented reality for urban design, transformable micro-housing for millennial, mobility-on-demand systems that create alternatives to private automobiles, and Urban Living Lab deployments in Hamburg, Andorra, Taipei, and Boston. Larson and researchers from his group received the “10-Year Impact Award” from UbiComp 2014. This is a “test of time” award for work that, with the benefit of hindsight, has had the greatest impact over the previous decade. Larson practiced architecture for 15 years in New York City, with design work published in Architectural Record, Progressive Architecture, Global Architecture, The New York Times, A+U, and Architectural Digest. The New York Times Review of Books selected his book, Louis I. Kahn: Unbuilt Masterworks (2000) as one of that year’s ten best books in architecture.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection*{Prof. Eran Ben Joseph}

{Class of 1922 Professor of Landscape Architecture and Urban Planning, head of the Department of Urban Studies and Planning at MIT from 2013 to 2020}
% 
\subsection*{Biography}
{Eran Ben-Joseph is the Class of 1922 Professor of Landscape Architecture and Urban Planning in the Department of Urban Studies and Planning at the Massachusetts Institute of Technology. Eran served as Head of the Department of Urban Studies and Planning at MIT from 2013 to 2020. His research and teaching areas include urban and physical design, standards and regulations, sustainable site planning technologies and urban retrofitting. He authored and co-authored the books: Streets and the Shaping of Towns and Cities, Regulating Place: Standards and the Shaping of Urban America, The Code of the City, RENEW Town and ReThinking a Lot. Eran worked as a city planner, urban designer and landscape architect in Europe, Asia, the Middle East and the United States on projects including new towns and residential developments, streetscapes, stream restorations, and parks and recreation planning. He has led national and international multi-disciplinary projects in Singapore, Barcelona, Santiago, Tokyo and Washington DC among other places. Eran holds degrees from the University of California at Berkeley and Chiba National University of Japan. Current Research: Urban Form and Health, Urban Form and the Aging Population, Urban Form and Ecological Models of Development, Urban Form and Manufacturing.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection*{Prof. Esteban Moro}

{Associate professor at the Universidad Carlos III de Madrid (Spain). Visiting Professor, Media Lab, Massachusetts Institute of Technology}
% 
\subsection*{Biography}
% 
{Prof. Esteban Moro is a visiting professor at the MIT Media Lab, an associate professor at the Universidad Carlos III de Madrid (Spain) and a member of the Joint Institute UC3M-Santander on Financial Big Data. Prof. Moro serve as a consultant for many public and private institutions and have held previous positions at the University of Oxford, Institute of Knowledge Engineering (Spain), and Instituto Mixto de Ciencias Matemáticas (Spain).Moro research is on applied mathematics, financial mathematics, viral marketing, and social networks. He received the "Shared University Award" from IBM in 2007 for modeling the spread of information in social networks and application to viral marketing and the Research Excellence Awards in 2013 and 2015 from the Carlos III University of Madrid. His recent work has been covered by many media outlets, including articles and interviews in El Pais, Muy Interesante, The Atlantic, The Washington Post, and The Wall Street Journal.}
