\newpage
\subsection{Publications, Projects, and Deployments Summary}
\subsubsection{Publications}

This dissertation will build on my recent work which has appeared in conferences and journals as listed below:

{\textbf{Noyman, A.}, Larson, K. (2020, April). DeepScope: HCI Platform for Generative Cityscape Visualization. In Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (pp. 1-9).}

{\textbf{Noyman, A.}, Doorley, R., Xiong, Z., Alonso, L., Grignard, A., Larson, K. (2019). Reversed urbanism: Inferring urban performance through behavioral patterns in temporal telecom data. Environment and Planning B: Urban Analytics and City Science, 46(8), 1480-1498.}

{Doorley, R., \textbf{Noyman, A.}, Sakai, Y., Larson, K. (2019). What’s your MoCho? Real-time Mode Choice Prediction Using Discrete Choice Models and a HCI Platform.}

{Alonso, L., Zhang, Y. R., Grignard, \textbf{A., Noyman}, A., Sakai, Y., ElKatsha, M., Larson, K. (2018, July). Cityscope: a data-driven interactive simulation tool for urban design. Use case volpe. In International conference on complex systems (pp. 253-261). Springer, Cham.}

{\textbf{Noyman, Ariel}, Yasushi Sakai, and Kent Larson. "Cityscope{AR}: urban design and crowdsourced engagement platform." arXiv preprint arXiv:1907.08586 (2019).}

{Grignard, A., Macià, N., Alonso Pastor, L.,\textbf{Noyman, A.}, Zhang, Y., Larson, K. (2018, July). Cityscope andorra: A multi-level interactive and tangible agent-based visualization. In Proceedings of the 17th International Conference on Autonomous Agents and MultiAgent Systems (pp. 1939-1940).
}
{\textbf{Noyman, A.}, Holtz, T., Kröger, J., Noennig, J. R., Larson, K. (2017). Finding places: HCI platform for public participation in refugees’ accommodation process. Procedia computer science, 112, 2463-2472.}

{Alrashed, T., Almalki, A., Aldawood, T., \textbf{Noyman, A.}, ... Alwabil, A. (2015). An observational study of usability in collaborative tangible interfaces for complex planning systems. Procedia Manufacturing, 3, 1974-1980.}

{\textbf{Noyman, A.} (2015). POWER/STRUCTURES: the Urban Form of Regulations (SM Thesis, Massachusetts Institute of Technology).}
% 
\begin{sidewaystable}
\subsubsection{CityScope Development and Deployments}
{This dissertation will build and extend CityScope projects developed at MIT, and deployed in real-world use-cases:}
\\\\
% \begin{table}[ht]
\centering
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{llllll}
\textit{project} & \textit{description} & \textit{medium}  &\textit{deployment} &\textit{date}  &  \\ \hline
CityScope Kendall Square & Urban Data Observatory & TUI & MIT Media Lab & 2013-2016 &  \\
CityScope Playground & Zoning simulator & TUI & APA, Cambridge City Council & 2014-2015&\\
CityScope BRT & Dudley Square & TUI, SW & Boston & 2014-2015\\
CityScope FindingPlaces & refugees’ accommodation process & TUI & Hamburg, Germany & 2015-2016\\
CityScopeAR & Augmented and Mixed Reality system for CityScope & AR/MR SW & Andorra, Volpe, BRT, APA & 2016-2019\\
CityScope Andorra & Telecom data observatory & TUI & Smart Cities Summit, Barcelona & 2016\\
CityScope Andorra & Urban Simulation and decision-making & TUI & Andorra La Vella & 2016-2017\\
CityScpoe LivingLine & Evaluating commercial street performance & TUI & Shanghai, China &  2017-2020\\
Reversed Urbanism & Human behavioral patterns through discrete telecom data & WEB & MIT Media Lab & 2018\\
CityScpoe MoCho & Modelling Mobility Mode Choice & WEB & MIT Media Lab & 2019\\
DeepScope & Predicting urban streetscapes through Generative models & TUI & MIT Media Lab & 2019\\
CityScope Champs-Élysées & Predicting interventions impact for Champs Élysées & TUI & Paris & 2019-2020\\
CityScope Corktown & Simulating real-time planning and mobility scenarios &  SW WEB & Ford, Detroit & 2019-2020\\

\hline
\textit{Work In Progress}\\
\hline
CityScope Volpe & City Simulation & TUI & MIT Media Lab & 2016-\\
CityScope Grasbrook & System for evaluating design competition proposals & TUI &  MIT and Hamburg & 2018-\\

CityIO & CityScope distributed backend & SW  &  MIT,  CSLs & 2016-\\

RoboScope & Robotic Interface for CityScope & TUI & Media Lab & 2019-\\

CityScopeJS & CityScope Distributed Web Platform
 & WEB & Across City Science Network & 2018-\\

\end{tabular}
\end{adjustbox}

\begin{minipage}{0.6\textwidth}
    \fontsize{8}{6}\selectfont
    \begin{enumerate}[topsep=1pt,itemsep=-1.5ex,partopsep=0.5ex,parsep=1ex]
        \item CSjs GRACIO
        \item CSjs Detroit Ford-Land
        \item CSjs Jerusalem
        \item CSjs Ho Chi Minh City District 4
        \item CSjs East Palo Alto
        \item CSjs `21 City Science Network course 
    \end{enumerate}
\end{minipage}


\end{sidewaystable}


\newpage


\subsubsection{CityScope Milestones}
{This list include milestones of the CityScope project, including exhibitions, awards, and mentions in popular media.}


\begin{itemize}

\item{CityScope was featured in “Report to The President - Technology and the Future of Cities”, President’s Council of Advisors on Science and Technology, 2016 (pp. 23)}

\item{CityScope project presented in the ‘Road Ahead’ exhibition at the Cooper Hewitt, NY 2019.}

\item{“FindingPlaces”: Public participation process using CityScope for data-driven housing allocation and planning for 80,000 refugees} 
    
\item{OECD Observatory for Public Sector Innovation (OPSI) and the United Arab Emirates (UAE) Mohammed Bin Rashid Centre for Government Innovation (MBRCGI) selected “FindingPlaces” out of 600 submission as a `Global Innovation': https://trends2019.oecd-opsi.org/}
    
\item{“FindingPlaces” won the United Nations - “Urban Act Award”, https://urbact.eu/finding-places}

\item{Poon, L. (2015, October 16). MIT's New Interactive LEGO Urban Tool Brings Transparency to Transit Planning. Retrieved July 26, 2020, from https://www.bloomberg.com/news/articles/2015-10-16/mit-s-new-interactive-lego-urban-tool-brings-transparency-to-transit-planning}

\item{Gillies, C. (2014, December 18). Lego: Can this most analogue of toys really be a modern urban planning tool? Retrieved July 26, 2020, from https://www.theguardian.com/cities/2014/dec/18/lego-toys-urban-planning-tool-architects-mit}

\item{Making ideas into reality at MIT's "Future Factory". (n.d.). Retrieved July 26, 2020, from https://www.cbsnews.com/news/60-minutes-mit-media-lab-making-ideas-into-reality-future-factory-2019-08-04/}
\item{Rob Matheson | MIT News Office. (2017, October 13). Small European nation becomes a "living lab" for urban innovation researchers. Retrieved July 26, 2020, from http://news.mit.edu/2017/european-nation-andorra-living-lab-media-lab-urban-innovation-1013}

\item{Science of Teams: Science of Teams. (2017, January 23). Science of Teams: How MIT Media Lab Builds Cities Using Lego and Augmented Reality. Retrieved July 26, 2020, from https://www.wired.com/video/watch/science-of-teams-mit-media-lab}

\item{Prevost, L. (2018, April 03). Building a Connected City From the Ground Up. Retrieved July 26, 2020, from https://www.nytimes.com/2018/04/03/business/smart-city.html}

\item{Wener-Fligner, Z. (2014, December 19). Lego makes a monochrome set targeted at architects. Retrieved July 26, 2020, from https://qz.com/315776/lego-for-grown-ups-the-toy-maker-is-targeting-architects-and-urban-planners/}

\item{GOLDSMITH, BOUSQUET, AR is Transforming Tech. What Can It Do for Cities?. Retrieved July 26, 2020, from https://datasmart.ash.harvard.edu/news/article/ar-transforming-tech-what-can-it-do-cities}

\item{LAURA ADLER,. (2016, AUGUST 29). SimCities: Can City Planning Mistakes Be Avoided Through Data-Driven Simulations? Retrieved July 26, 2020, from https://www.govtech.com/data/SimCities-Can-City-Planning-Mistakes-Be-Avoided-Through-Data-Driven-Simulations.html}

\item{Garcia, J. (2018, July 08). El MIT usa fichas Lego y big data para saber dónde dar futuro a los inmigrantes. Retrieved July 26, 2020, from https://www.lainformacion.com/tecnologia/el-mit-salva-inmigrantes-con-fichas-lego-gracias-al-big-data-sabe-donde-deben-ser-situados-en-una-ciudad/6351916/}

\item{Woldin, P. (2016, March 02). „City-Scope": Mit Legosteinen Flüchtlingsunterkünfte finden - WELT. Retrieved July 26, 2020, from https://www.welt.de/regionales/hamburg/article152836431/Mit-Legosteinen-Fluechtlingsunterkuenfte-finden.html}

\end{itemize}

\newpage