\section{Contributions}
 {
  This thesis contributes to urban modeling and simulation, HCI, Decision Support Systems, urban decision-making and consensus-building in several aspects:

  \begin{itemize}
        \item The development of a scalable, real-time, socio-technical urban modeling and simulation platform.
        \item The development of a system and a schema for urban analytics through distributed computation system.
        \item The development of real-time, explicit and implicit spatial analytics modules to asses urban behavior, mobility, and performance.
        \item Deployment of dozens of CityScope platforms around the world, some of which in real-world city-planning contexts.
        \item The creation of community of users, developers, contributes, and researchers building and using CityScope worldwide.
  \end{itemize}
 }

\section{Publications, Projects, and Deployments}\label{sec:publications-projects-deployments}

{
      The following is a list of publications, projects, and deployments of the CityScope platform, as well as corresponding research in Urban Sciences, Spatial Analytics, and mutual fields.

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

      \input{chapters/introduction/pubs.tex}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

      \input{chapters/introduction/cs_projects_table.tex}
}



\subsection{CityScope Milestones}

{This list includes CityScope milestones, exhibitions, awards, and mentions in the press and popular media:

      \begin{itemize}

            \item{CityScope was featured in “Report to The President - Technology and the Future of Cities”, President's Council of Advisors on Science and Technology, 2016 (pp. 23)}

            \item{CityScope project presented in the `Road Ahead' exhibition at the Cooper Hewitt Museum, NYC, 2019.}

            \item{“FindingPlaces”: Public participation process using CityScope for data-driven housing allocation and planning for 80,000 refugees}

            \begin{itemize}
                  \item{
                              OECD Observatory for Public Sector Innovation (OPSI) and the United Arab Emirates (UAE) Mohammed Bin Rashid Centre for Government Innovation (MBRCGI) selected “FindingPlaces” out of 600 submission as a `Global Innovation': \url{https://trends2019.oecd-opsi.org/}
                        }

                  \item{
                              “FindingPlaces” won the United Nations - “Urban Act Award”, \url{https://urbact.eu/finding-places}
                        }
            \end{itemize}

            \item{
                        Poon, L. (2015, October 16). MIT's New Interactive LEGO Urban Tool Brings Transparency to Transit Planning. Retrieved July 26, 2020, from \url{https://www.bloomberg.com/news/articles/2015-10-16/mit-s-new-interactive-lego-urban-tool-brings-transparency-to-transit-planning}
                  }

            \item{
                        Gillies, C. (2014, December 18). LEGO: Can this most analogue of toys really be a modern urban-planning tool? Retrieved July 26, 2020, from \url{https://www.theguardian.com/cities/2014/dec/18/lego-toys-urban-planning-tool-architects-mit}
                  }

            \item{
                        Making ideas into reality at MIT's "Future Factory". (n.d.). Retrieved July 26, 2020, from \url{https://www.cbsnews.com/news/60-minutes-mit-media-lab-making-ideas-into-reality-future-factory-2019-08-04/}
                  }

            \item{
                        Rob Matheson | MIT News Office. (2017, October 13). Small European nation becomes a "living lab" for urban innovation researchers. Retrieved July 26, 2020, from \url{http://news.mit.edu/2017/european-nation-andorra-living-lab-media-lab-urban-innovation-1013}
                  }

            \item{
                        Science of Teams: Science of Teams. (2017, January 23). Science of Teams: How MIT Media Lab Builds Cities Using LEGO and Augmented Reality. Retrieved July 26, 2020, from \url{https://www.wired.com/video/watch/science-of-teams-mit-media-lab}
                  }

            \item{
                        Prevost, L. (2018, April 03). Building a Connected City From the Ground Up. Retrieved July 26, 2020, from \url{https://www.nytimes.com/2018/04/03/business/smart-city.html}
                  }

            \item{
                        Wener-Fligner, Z. (2014, December 19). LEGO makes a monochrome set targeted at architects. Retrieved July 26, 2020, from \url{https://qz.com/315776/lego-for-grown-ups-the-toy-maker-is-targeting-architects-and-urban-planners/}
                  }

            \item{
                        GOLDSMITH, BOUSQUET, AR is Transforming Tech. What Can It Do for Cities?. Retrieved July 26, 2020, from \url{https://datasmart.ash.harvard.edu/news/article/ar-transforming-tech-what-can-it-do-cities}
                  }

            \item{
                        LAURA ADLER,. (2016, AUGUST 29). SimCities: Can City-planning Mistakes Be Avoided Through Data-Driven Simulations? Retrieved July 26, 2020, from \url{https://www.govtech.com/data/SimCities-Can-City-Planning-Mistakes-Be-Avoided-Through-Data-Driven-Simulations.html}
                  }

            \item{
                        Garcia, J. (2018, July 08). El MIT usa fichas LEGO y big data para saber dónde dar futuro a los inmigrantes. Retrieved July 26, 2020, from \url{https://www.lainformacion.com/tecnologia/el-mit-salva-inmigrantes-con-fichas-lego-gracias-al-big-data-sabe-donde-deben-ser-situados-en-una-ciudad/6351916/}
                  }

            \item{
                        Woldin, P. (2016, March 02). „City-Scope": Mit Legosteinen Flüchtlingsunterkünfte finden - WELT. Retrieved July 26, 2020, from \url{https://www.welt.de/regionales/hamburg/article152836431/Mit-Legosteinen-Fluechtlingsunterkuenfte-finden.html}
                  }

      \end{itemize}
}
