{
\textbf{Noyman, A.}, Larson, K. (2020, April). DeepScope: HCI Platform for Generative Cityscape Visualization. In Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (pp. 1-9).
}

{
\textbf{Noyman, A.}, Doorley, R., Xiong, Z., Alonso, L., Grignard, A., Larson, K. (2019). Reversed urbanism: Inferring urban performance through behavioral patterns in temporal telecom data. Environment and Planning B: Urban Analytics and City Science, 46(8), 1480-1498.
}

{
Doorley, R., \textbf{Noyman, A.}, Sakai, Y., Larson, K. (2019). What's your MoCho? Real-time Mode Choice Prediction Using Discrete Choice Models and a HCI Platform.
}

{
Alonso, L., Zhang, Y. R., Grignard, \textbf{A., Noyman}, A., Sakai, Doorley, R., Y., ElKatsha, M., Larson, K. (2018, July). Cityscope: a data-driven interactive simulation tool for urban-design. Use-case volpe. In International conference on complex systems (pp. 253-261). Springer.
}

{
\textbf{Noyman, Ariel}, Yasushi Sakai, and Kent Larson. "Cityscope{AR}: urban-design and crowdsourced engagement platform." arXiv preprint arXiv:1907.08586 (2019).
}

{
Grignard, A., Macià, N., Alonso Pastor, L.,\textbf{Noyman, A.}, Zhang, Y., Larson, K. (2018, July). Cityscope andorra: A multi-level interactive and tangible agent-based visualization. In Proceedings of the 17th International Conference on Autonomous Agents and MultiAgent Systems (pp. 1939-1940).
}

{
\textbf{Noyman, A.}, Holtz, T., Kröger, J., Noennig, J. R., Larson, K. (2017). Finding places: HCI platform for public participation in refugees’ accommodation process. Procedia computer science, 112, 2463-2472.
}

{
Alrashed, T., Almalki, A., Aldawood, T., \textbf{Noyman, A.}, ... Alwabil, A. (2015). An observational study of usability in collaborative tangible interfaces for complex planning systems. Procedia Manufacturing, 3, 1974-1980.
}

{
\textbf{Noyman, A.} (2015). POWER/STRUCTURES: the Urban Form of Regulations (SM Thesis, Massachusetts Institute of Technology).
}