\section*{Contextual Area:\\Transformation and Consensus}
% 
\subsection*{Examiner}
Prof. Eran Ben Joseph\\
Professor, Head of the Department of Urban Studies and Planning\\
Massachusetts Institute of Technology
% 
\subsection*{Biography}
Eran Ben-Joseph is a Professor and Head of the Department of Urban Studies and Planning at the Massachusetts Institute of Technology. His research and teaching areas include urban and physical design, standards and regulations, sustainable site planning technologies and urban retrofitting. He authored and co-authored the books: Streets and the Shaping of Towns and Cities, Regulating Place: Standards and the Shaping of Urban America, The Code of the City, RENEW Town and ReThinking a Lot. Eran worked as a city planner, urban designer and landscape architect in Europe, Asia, the Middle East and the United States on projects including new towns and residential developments, streetscapes, stream restorations, and parks and recreation planning. He has led national and international multi-disciplinary projects in Singapore, Barcelona, Santiago, Tokyo and Washington DC among other places. Eran holds degrees from the University of California at Berkeley and Chiba National University of Japan. Current Research: Urban Form and Health, Urban Form and the Aging Population, Urban Form and Ecological Models of Development, Urban Form and Manufacturing.
% 
\subsection*{Description}

\textit{``it is likely that participation in formulating policies might be very different from the past when futures were dictated by the elite, primarily because of its access to information."} [Batty M., et al, 2012]
\newline
The \textbf{Contextual research area} explores socio-technical approaches to urban planning, focusing on alternative methodologies, tools and processes for urban decision-making. Readings in this section observe two themes of the CityScope process: urban \textbf{transformation} and \textbf{consensus}.
\begin{itemize}
\item \textbf{transformation}: how to rapidly and iteratively evaluate urban 'what-if' scenarios? This section will explore the emergence of Computer Aided Design since the 1980's till today. It will expand on the history and theory of Tangible User Interfaces and Human-Computer Interaction in the context of urban design and planning. 
\item \textbf{consensus}: how to construct a multi-stakeholders decision-making processes?
This subsection explores novel methods and tools for collaborative design, community engagement and public participation in urban planning processes.  

\end{itemize}
% 
\subsection*{Written Requirement}
The written requirement will consist of a 24-hour take-home examination to be administered and evaluated
by Prof. Eran Ben-Joseph.\par
% 
\textbf{Signature}\hspace{0.5cm} \makebox[2in]{\hrulefill}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Readings in the Contextual Area}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Origins of CHI}
\begin{bibunit}[unsrt]
\nocite{*}
\putbib[contextual/CONTEXT_TUI]
\end{bibunit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Evaluating Urban Transformation}
\begin{bibunit}[unsrt]
\nocite{*}
\putbib[contextual/CONTEXT_urbanCHI]
\end{bibunit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Constructing Consensus}
\begin{bibunit}[unsrt]
\nocite{*}
\putbib[contextual/CONTEXT_CONSENSUS]
\end{bibunit}