

\section*{Technical Area:\\Insight and Prediction}
% 
\subsection*{Examiner}
Prof. Esteban Moro\\
Associate professor at the Universidad Carlos III de Madrid (Spain)\\
Visiting Professor, Media Lab, Massachusetts Institute of Technology
% 
\subsection*{Biography}
% 
Prof. Esteban Moro is a visiting professor at the MIT Media Lab, an associate professor at the Universidad Carlos III de Madrid (Spain) and a member of the Joint Institute UC3M-Santander on Financial Big Data. Prof. Moro serve as a consultant for many public and private institutions and have held previous positions at the University of Oxford, Institute of Knowledge Engineering (Spain), and Instituto Mixto de Ciencias Matemáticas (Spain).\par
Moro\'s research is on applied mathematics, financial mathematics, viral marketing, and social networks. He received the "Shared University Award" from IBM in 2007 for modeling the spread of information in social networks and application to viral marketing and the Research Excellence Awards in 2013 and 2015 from the Carlos III University of Madrid. His recent work has been covered by many media outlets, including articles and interviews in El Pais, Muy Interesante, The Atlantic, The Washington Post, and The Wall Street Journal.
% 
\subsection*{Description}
% 
\textit{``In the history of urban studies and planning, most theory and applications have focused on the long term (...) Of course, many groups are concerned with how cities function more routinely over the day but this has not been considered part of urban planning(...)"}[Batty, 2013]\newline 

How can urban-data and spatial analytics inform a New Urban Process? The \textbf{Technical research area} expands on recent geo-spatial and urban data-science research. It focuses on two themes of the CityScope process, \textbf{insight} and \textbf{prediction}.
\begin{itemize}
    \item \textbf{insight}: How to collect and analyse urban data to understand current conditions?
    Readings in this subsection will explore Location Based Services and geo-tagged data, remote sensing and tracking, spatial-analysis and data processing.
    \item \textbf{prediction}: Turning urban analytics into predictions. Readings in this subsection will explore the effort to predict the effects of planning and spatial transformations on various urban layers, from transportation and real-estate to inequality and human dynamics.
    It will explore `causality' in the context of urban planning, and the way \textit{what if} scenarios should be constructed, tested and validated.


    
\end{itemize}
Finally, this section will include readings on the limitations and risks of using urban data, from the perspective of privacy and accuracy. 

% 
\subsection*{Written Requirement}
The written requirement will consist of a submitted academic paper to be administered and evaluated by Prof. Esteban Moro.\par
% 
\textbf{Signature}\hspace{0.5cm} \makebox[2in]{\hrulefill}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection*{Readings in the Contextual Area}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Behavioral Patterns and Urban Dynamics}
\begin{bibunit}[unsrt]
\nocite{*}
\putbib[technical/TECH_lbs]
\end{bibunit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Urban Modelling \& Prediction}
\begin{bibunit}[unsrt]
\nocite{*}
\putbib[technical/TECH_models]
\end{bibunit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%