\section*{Acknowledgments}
 {
  I first joined Kent Larson's group as a student in his `Beyond Smart Cities' workshop in 2014. At the time, I did not know what Smart Cities meant, why we need to move \textit{beyond} them, and what \textit{science} had to do with all of that. Within a couple of weeks, I knew I'll be shifting my Master program into Kent's group. A few months later, Kent would offer me to lead the founding of a new City Science lab in Hamburg; the rest of the story is laid out in this thesis.
  \newline
  I cannot be grateful enough for Kent's generosity, kindness, and his belief in people. I learned many things from Kent, but most importantly is that great things come from the least expected people, if you only create the conditions for them to do so. I am grateful for his mentoring, guidance, and friendship during these years.
  \newline
  I wish to thank my committee. Prof. Eran Ben-Joseph has been a key supporter, motivator, and advisor during my entire journey at MIT. His work on the intersection of technology, urbanism, law, and design, was a major inspiration to both my master's thesis and this dissertation.
  I have learned a lot from countless interactions and conversations with Prof. Esteban Moro. Coming from pure theoretical physics into the unholiness of the built environment, Esteban showed me the beauty of applying sophisticated science to the most pedestrian challenges.
  \newline
  Many mentors have been instrumental to my work and growth.
  \newline
  I thank my many friends, collaborators, and colleagues at the City Science Network worldwide, for their wisdom, hospitality, and shared passion for better cities. Building a vibrant network of City Science Labs, from Southeast Asia to South America, has been one the best experiences of my tenure at MIT. Specifically, I'd like to thank Prof. Gesa Zimmer and Prof. Jörg Noennig from the HafenCity University in Hamburg, for allowing me to be part of the founding team of the CityScienceLab. Since 2015, the entire CityScienceLab team has been a tremendous force in my journey, especially (in alphabetical order) Andre, Frank, Holger, Imanuel, Jan Ba., Jan Be., Jesús, Katrin, Nina, Sarah, Till, and Tobi.
  \newline
  All of the projects mentioned in this thesis were created by the wonderful members of the MIT City Science group, alongside collaborators from the City Science Network, and with the help of many external partners\footnote{The first version of cityIO was create by Nikita Samsonov (MIT EECS) in 2015. Since then, cityIO is maintained by Yasushi Sakai (MIT Media Lab). CityScopeAR was conceived with the help of Nikita Samsonov (MIT EECS) and Dalma Foldesi (MIT SA+P). Yuke Zheng (Harvard University) made significant contributions to the development of CityScopeJS. For individual contributor information, please see references in Section \eqref{sec:publications-projects-deployments}.}. I would like to thanks the core members of the CityScope team (in an alphabetical order): Arnaud, Cris, Luis, Markus, Ronan, Ryan, and Yasushi; None of the work presented here would have been possible without you. Arnaud and Luis: Thank you for being my right and left hand, interchangeably. Ronan: Thank you for leading my in mystical ways of Data Science; May your models always fit. Countless other contributes have made CityScope better each day: from thousands of CityScope users worldwide, through anonymized open-source contributions, to makeshift CityScope creators, they all share the same hope for better cities. Thank you all.

  \bigskip
  \begin{center}
      $\sim$
  \end{center}
  \bigskip

  I am grateful for my family. My parents, Shlomit and Moshe, brothers Johnathan and Gilad, and the entire family, for their unconditional love and support during these years. I would like to commemorate my late grandmother Bina, who's wisdom and wonder motivated my journey.

  \bigskip

  To Arad and Ori, for reminding me of what's important. May we leave better cities for your future.

  \bigskip
  To Roni, who took me out my comfort zone, and created comfort whenever I needed it. None of this would have been possible without you.
 }